\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. This is an abstract. 
\end{abstract}

\begin{keywords}
  Neural Architecture Search, Deep Meta-Reinforcement Learning, Image Classification
\end{keywords}

%Todo: check difference between citep and citet